BLAST

### 2025-03-30 episodes/blast.Rmd
Corrected two links and a typo in BLAST exercise

The whole exercise is based on RpoB, the [&Beta;-subunit of the bacterial RNA polymerase](https://en.wikipedia.org/wiki/RpoB). This protein is essential to the cell, and present in all bacteria and plastids. It is also very conserved, and thus suitable for deep-scale phylogenies.

@@

Databases available at UPPMAX are described here: https://www.uppmax.uu.se/resources/databases/blast-databases/. The `blast_databases` module implies that you don't need to specify where the databases are located on the file system. In detail, it sets the `BLASTDB` variable to the right folder. You can see it by typing `echo $BLASTDB` in the terminal.

@@

Taxonomy resources at UPPMAX are described here: https://www.uppmax.uu.se/resources/databases/ncbi-taxonomy-databases

>>>>

The whole exercise is based on RpoB, the [&beta;-subunit of the bacterial RNA polymerase](https://en.wikipedia.org/wiki/RpoB). This protein is essential to the cell, and present in all bacteria and plastids. It is also very conserved, and thus suitable for deep-scale phylogenies.

@@

Databases available at UPPMAX are described here: https://docs.uppmax.uu.se/databases/blast/. The `blast_databases` module implies that you don't need to specify where the databases are located on the file system. In detail, it sets the `BLASTDB` variable to the right folder. You can see it by typing `echo $BLASTDB` in the terminal.

@@

Taxonomy resources at UPPMAX are described here: https://docs.uppmax.uu.se/databases/ncbi/
